Using the internal language of toposes in algebraic geometry

### 2015-09-21 abstract-ihes2015.tex
Final version

\title{Using the internal language of toposes in algebraic geometry}
\author{Ingo Blechschmidt}
\email{ingo.blechschmidt@math.uni-augsburg.de}
\pagestyle{empty}

@@

\begin{abstract}
  In algebraic geometry, one often studies schemes from a local or relative
  point of view. We describe how the internal language of certain
  toposes, the associated petit and gros Zariski toposes of a scheme, can be
  used to give simpler definitions and more conceptual proofs of the basic
  notions and observations in algebraic geometry.

  The starting point is that sheaves of rings and sheaves of modules look
  just like plain rings respectively modules from the internal point of view.
  In this way, some concepts and statements of scheme theory can be reduced to
  concepts and statements of intuitionistic linear algebra.

@@

  A particularly interesting task is to internalize the ``relative spectrum''
  construction of algebraic geometry, which given a quasicoherent sheaf of algebras
  on a scheme~$X$ yields a scheme over~$X$. From the internal point of
  view, this construction should simply reduce to a intuitionistically sensible
  variant of the ordinary construction of the spectrum of a ring, but it turns
  out that this expectation is too naive and that a refined approach is
  necessary.
\end{abstract}

\maketitle

>>>>

\title{Using the internal language of toposes in algebraic geometry}
\author{Ingo Blechschmidt}
\email{ingo.blechschmidt@math.uni-augsburg.de}

@@

\begin{abstract}
  We describe how the internal language of certain
  toposes, the associated petit and gros Zariski toposes of a scheme, can be
  used to give simpler definitions and more conceptual proofs of the basic
  notions and observations in algebraic geometry.
  % This is useful for studying schemes from a local or relative point of view.

  The starting point is that, from the internal point of view, sheaves of rings
  and sheaves of modules look just like plain rings and plain modules.
  In this way, some concepts and statements of scheme theory can be reduced to
  concepts and statements of intuitionistic linear algebra.

@@

  A particularly interesting task is to internalize the
  construction of the relative spectrum, which, given a quasicoherent sheaf of algebras
  on a scheme~$X$, yields a scheme over~$X$. From the internal point of
  view, this construction should simply reduce to an intuitionistically sensible
  variant of the ordinary construction of the spectrum of a ring, but it turns
  out that this expectation is too naive and that a refined approach is
  necessary.
\end{abstract}

\maketitle
\thispagestyle{empty}
